\documentclass[12pt]{report}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage{todonotes}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{algorithmic}

\title{House Prices: Advanced Classification Techniques}

\author{
  Nguyen Duc Thien, 20168806\\
  \texttt{thien.nd168806@sis.hust.edu.vn}
  \and
  Trinh Ngoc Khang, 2016xxxx\\
  \texttt{khang.tn16xxxx@sis.hust.edu.vn}
  \and
  Le Duc Thang, 2016xxxx\\
  \texttt{thang.ld16xxxx@sis.hust.edu.vn}
  \and
  Vu Hoang Duc Hieu, 20168199\\
  \texttt{hieu.vhd168199@sis.hust.edu.vn}
}

\begin{document}

\begin{titlepage}
  \maketitle
\end{titlepage}

\begin{abstract}
  Now  a  days  house  resale  is  majorly  seen  in  metro  cities.
  The market demand for housing is always increasing every year due to  increase
  in  population  and  migrating  to  other  cities  for  their  financial  purpose.
  Prediction  of  house  resale  price  for  long-term  temporary  basis  is  important
  especially  for  the  people  who  stays    who will stay the long time period but not permanent
  and the people who  do  not  want  to  take  any  risk  during  the  house  construction.
  In    this  paper,  the  resale  price  prediction  of  the  house  is  done  using  different
  classification  algorithms  like  Logistic  regression,  Decision  tree,  Naive  Bayes  and
  Random  forest  is  used  and  we  use  AdaBoost  algorithm  for  boosting  up  the  weak  learners
  to  strong  learners.  Several factors  that are affecting the house resale price includes
  the physical  attributes,  location  as  well  as  several  economic  factors  persuading
  at   that   time.   Here   we   consider   accuracy   as   the   performance metrics for
  different datasets and these algorithms are applied and compared to discover the most appropriate
  method that can  be  used  the  reference  for  determining  the  resale  price  by  the  sellers.
  Index  Terms—  House  Resale  Price,  Prediction,  Random  Forest,    AdaBoost, Naïve Bayes.

  \emph{Paraphase}


\end{abstract}

\tableofcontents

\chapter{Introduction}
The value of a home is well known as a combination of a large variety  of  options.  
Therefore,  the  prediction  of  home  price  presents a novel set of challenges. 
Though an oversized variety of   space   units   are   dedicated   to   the   present   task,  
 their   performance  and  applications  are  restricted  by  a  really  long  delay  within  
 the  handling  of  data,  the  dearth  of  real-world  settings and so the inadequacy of 
 choices for housing. Our aim is  to  predict  the  value  of  the  house  marketing  mistreatment  
 classification techniques during this paper. Most of the present studies have concentrated on 
 breakdown the distraction of the prediction  of  house  costs.  Several  theories  are  born  
 as  an  outcome   of   the   analysis   work   committed   by   completely   different 
 researchers around the world. This paper picks up the most recent prediction analysis 
 to assist economic predictors to use  it.  It  provides  a  summary  of  the  prediction 
markets  and,  together,  the  present  markets  that  build  it  easier  to  predict  the  market.

\todo{gioi thieu ve bai toan}

\chapter{Related work}
\todo{gioi thieu cac bai toan lien quan}
cac bai toan, paper lien quan
\chapter{Algorithms}

\section{Naive bayer}
Cong thuc naive bayer dua tren ly thuyet xac suat

\section{Decision Tree}
Cay quyet dinh - mot mo hinh dua ra quyet dinh dua tren information gain

\section{Logistic Regression}
Mot thuat toan machine learning

\section{Multi Layer Perception}
Mot mo hinh neural network

\chapter{Result on Kaggle Dataset}
\todo{noi ve dataset}
chaper nay de noi ve ket qua training va data set 

\chapter{Conclusion}
ket luan ve bai tona
\end{document}
